%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{System administrator} % Job title
{Betiator gaming technologies} % Organization
{Athens, Greece} % Location
{Aug. 2015 - Oct. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and implemented a cluster based on Docker, Mesos, Marathon and Zookeeper. Upgraded to DC/OS later.}
\item {Setting up and monitoring Couchbase clusters.}
\item {Automation and continuous development with Jenkins, Python and BASH}
\item {Networking and security: Mikrotik, HAProxy, CentOS}
\item {\bfseries{Technologies:} Docker, DC/OS, J2EE, Wildfly, Redis, NodeJS, Jenkins, Couchbase, Hadoop}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Linux administrator (intern)} % Job title
{IP Digital} % Organization
{Thessaloniki, Greece} % Location
{Oct. 2014 - Dec. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {High availability cluster: proxmox and ovirt.}
\item {Backup and storage on Freenas and zfs.}
\item {Automation and logging with BASH scripts}
\item {\bfseries{Technologies:} ovirt, unraid, freenas, nas4free, zfsguru, nappit, omnios, openindiana, nexenta and proxmox}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Laboratory Assistant (Rewarding Scholarship)} % Job title
{Laboratory of Digital Systems and Computer Architecture} % Organization
{Kozani, Greece} % Location
{Mar. 2014 - Jun. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Supervising and helping students overcome programming and technical difficulties on the courses}
\begin{itemize}
\item {Operating systems}
\item {Systems of parallel and distributed execution}
\item {Digital design}
\end{itemize}
\end{cvitems}
}

%------------------------------------------------

\cventry
{University Librarian (Rewarding Scholarship)} % Job title
{University Of Western Macedonia} % Organization
{Kozani, Greece} % Location
{Mar. 2013 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://lib.uowm.gr/}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}